---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Populationpack2016

<!-- badges: start -->
<!-- badges: end -->

The goal of Populationpack2016 is to analyze information about population based on number of families, owners, tenants and residential units of all neighbourhoods in Mashhad, Iran.
By clicking on [here](https://niloofarnl.github.io/Populationpack2016/reference/population_density.html) you can have access to the vignettes.

## Installation

You can install the development version of Populationpack2016 like so:

```
knitr::opts_chunk$set(message = FALSE)
if(!require(remotes)){
    install.packages("remotes")
    library(remotes)
}
remotes::install_github("NiloofarNL/Populationpack2016")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(Populationpack2016)
library(ggplot2)
summary(Population2016)

## basic example code
```

```{r fig-Tenants-and-Population, echo = FALSE, outwith="1.0\\linewidth", fig.cap="\\label{fig-Tenants-and-Population} Relationship between Tenants  and Population"}
ggplot(data = Population2016, aes(x = Population, y = Tenants)) +
  geom_point() +
  ggtitle("Tenants  and Population") +
  xlab("Population") +
  ylab("Tenants")

```


```{r fig-Owners-and-Population, echo = FALSE, outwith="1.0\\linewidth", fig.cap="\\label{fig-Owners-and-Population} Relationship between Owners  and Population"}
ggplot(data = Population2016, aes(x = Population, y = Owners)) +
  geom_point() +  
  ggtitle("Owners  and Population") +
  xlab("Population") +
  ylab("Owners")
```
